Practical Optional Types for Clojure

### 2015-02-25 overview.tex
formatting examples

\begin{exmp}
\inputminted[firstline=6,lastline=8]{clojure}{code/demo/src/demo/parent3.clj}
\end{exmp}

@@

\begin{Code}
\begin{exmp}
\begin{minted}{clojure}
(ann rep [Any -> String])
(defmulti rep class)
(defmethod rep Keyword [x] (str (name x)))
(defmethod rep Number [x] (str (inc x)))

(rep :a) ;=> "a"
(rep 1)  ;=> "2"
\end{minted}
\end{exmp}
\end{Code}
Typed Clojure does not statically ensure multimethod calls dispatch successfully---
\clj{(rep "a")} type checks but throws a runtime error.

The flexibility of \clj{isa?} is key to the generality of multimethods. 
We can dispatch on the \clj{:op} key 
of our HMap AST \clj{Expr}.
Keywords are functions that look themselves up in their argument, so \clj{:op}
is our dispatch function.
\begin{Code}
\begin{exmp}
\inputminted[firstline=4,lastline=23]{clojure}{code/demo/src/demo/eg5.clj}
\end{exmp}
\end{Code}
The destructuring syntax \clj{(fn [{:keys [val] :as m}] ...)} binds
\clj{m} to the value of the first argument, and \clj{val} to \clj{(:val m)}.

>>>>

\begin{exmp}
\inputminted[firstline=5,lastline=8]{clojure}{code/demo/src/demo/parent3.clj}
\end{exmp}

@@

\begin{Code}
\begin{exmp}
\inputminted[firstline=5,lastline=11]{clojure}{code/demo/src/demo/rep.clj}
\end{exmp}
\end{Code}
Typed Clojure does not statically ensure multimethod calls dispatch successfully---
\clj{(rep "a")} type checks but throws a runtime error.

The flexibility of \clj{isa?} is key to the generality of multimethods. 
We can dispatch on the \clj{:op} key 
of our HMap AST \clj{Expr}.
Keywords are functions that look themselves up in their argument, so \clj{:op}
is our dispatch function.
\begin{Code}
\begin{exmp}
\inputminted[firstline=5,lastline=23]{clojure}{code/demo/src/demo/eg5.clj}
\end{exmp}
\end{Code}
The destructuring syntax \clj{(fn [{:keys [val] :as m}] ...)} binds
\clj{m} to the value of the first argument, and \clj{val} to \clj{(:val m)}.
